Approximation as Differentiation

### 2025-04-02 notes/sec/cmon-enriched.tex
No need to mention that CMon is symmetric closed.

\begin{definition}[Category of commutative monoids]
Define $\CMon$ to be the category whose objects are the commutative monoids $A$ and morphisms $A \to B$ are
the commutative monoid homomorphisms.
\end{definition}

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object, monoidal
product $A \tensor B$ given by the Cartesian product of $A$ and $B$, and braiding given by the isomorphism $A
\times B \iso B \times A$. $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

>>>>

\begin{definition}[Category of commutative monoids]
Define $\CMon$ to be the category whose objects $A$ are the commutative monoids $A$ and morphisms $f: A \to B$
are the commutative monoid homomorphisms.
\end{definition}

$\CMon$ is closed monoidal, with the trivial one-element monoid $\One$ as terminal object and monoidal product
$A \tensor B$ given by the Cartesian product $A \times B$. $\CMon$ is complete and cocomplete, inheriting all
limits and colimits from $\Set$.
